Supplementary material for\\ A Benchmark of Named Entity Recognition Approaches in Historical Documents\\ Application to 19$^{th}$ Century French Directories

### 2022-01-20 src-latex/parts/20-related-work.tex

\textbf{Tesseract} 4.1.1 (newest version: 5, released Nov. 2021)
\textbf{Pero OCR} version from git repo, master branch updated on Sep 15, 2021
\textbf{Kraken}

\textbf{Spacy} is a software library that offers NLP components assembled in modular pipelines specialised by language.
Although BERT is available in the latest version of SpaCy (v3), the pipeline for French does not provide a NER layer at the time of our experiments (jan. 2022).
Hence, we rely on SpaCy's ad hoc pipeline trained on French corpora and capable of named entity recognition.
% deep-sequoia and wikiner-fr, capable of named entity recognition.\textit{fr\_core\_news\_lg}\footnote{https://spacy.io/models/fr} trained two corpora in French: deep-sequoia and wikiner-fr, capable of named entity recognition.
The global architecture of these pipelines have not been yet published but are explained by the developers on their website.
Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}.
The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}.
As words are processed sequentially, their vectors are concatenated with those of the last known entities to encode the nearby predicted semantics.
The classification layer relies on a finite-state machine whose transition probabilities are learned using a multilayer perceptron.
% \bertrand{Drop the next sentences if we need space}
% In 2018~\cite{won2018} evaluated SpaCy's NER ability to detect place names in five corpora of ancient letters written in English.
% They measured an average F1 score of 0.57.
% The SpaCy developers claim an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.
%For our experiments, the French model \textit{fr\_core\_news\_lg} is fine-tuned using our ground truth corpus.

\textbf{Transformers / Bert / Hugging face}
Language model based on \textit{Transformers} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pretrained in an unsupervised way on historical texts for domain adaptation.
As the directories are written in French, we chose the language model CamemBERT \cite{martin-etal-2020-camembert}, a Transformer model trained on a French corpus.
\joseph{plutôt tourner ça pour dire qu'il existe des modèles FR / qu'on est limités par la dispo de modèles FR pré-entraînés ?}

\Cref{fig.protocol} depicts the evaluation protocol used to assess the OCR and NER systems.

>>>>

\textbf{Tesseract} 4.1.1 (newest version: 5, released Nov. 2021)

\textbf{Pero OCR} version from git repo, master branch updated on Sep 15, 2021

\textbf{Kraken}

\textbf{SpaCy} is a software library that offers NLP components assembled in modular pipelines specialised by language.
Although BERT is available in the latest version of SpaCy (v3), the pipeline for French does not provide a NER layer at the time of our experiments (jan. 2022).
Hence, we rely on SpaCy's ad hoc pipeline trained on French corpora and capable of named entity recognition.
% deep-sequoia and wikiner-fr, capable of named entity recognition.\textit{fr\_core\_news\_lg}\footnote{https://spacy.io/models/fr} trained two corpora in French: deep-sequoia and wikiner-fr, capable of named entity recognition.
The global architecture of these pipelines have not been yet published but are explained by the developers on their website.
Words are first encoded into local context-aware embeddings using a window-based CNN similar to~\cite{collobert2011}.
The decision layer is an adaptation of the transition-based model presented in~\cite{lample2016}.
As words are processed sequentially, their vectors are concatenated with those of the last known entities to encode the nearby predicted semantics.
The classification layer relies on a finite-state machine whose transition probabilities are learned using a multilayer perceptron.
% \bertrand{Drop the next sentences if we need space}
% In 2018~\cite{won2018} evaluated SpaCy's NER ability to detect place names in five corpora of ancient letters written in English.
% They measured an average F1 score of 0.57.
% The SpaCy developers claim an accuracy of 0.85 for the English NER pipeline \textit{en\_core\_web\_lg} on the OntoNotes 5.0 corpus\footnote{https://spacy.io/usage/facts-figures}.
%For our experiments, the French model \textit{fr\_core\_news\_lg} is fine-tuned using our ground truth corpus.

\textbf{CamemBERT}
Language model based on \textit{Transformers} \cite{vaswani2017attention}, like BERT \cite{devlin2018bert}, have become a new paradigm for NER\cite{li2020}. 
The learned embeddings can be used as distributed representations for input instead of traditional embeddings like Google Word2Vec, and they can be further fine-tuned for NER by adding an additional output layer. 
They can also be pretrained in an unsupervised way on historical texts for domain adaptation.
CamemBERT \cite{martin-etal-2020-camembert}, is a weel-known French language model derived from BERT, of which there are already trained versions for the NER task on the Hugging Face library.

The Figure \ref{fig.pipeline} depicts the evaluation protocol used to assess the combined performance of these OCR and NER systems.
